Analysis Script

### 2025-05-01 code/analysis-code/statisitical-analysis.qmd
Part 6

# Check date ranges
range(train_data$date)
range(test_data$date)

Recipe setting for modeling
```{r}
# Recipe for baseline model
recipe_baseline <- recipe(new_cases ~ pop_density + lag_1 + lag_7 + lag_14, data = data)

# Recipe with all predictors
recipe <- recipe(new_cases ~ pop_density +
                  retail_and_recreation_percent_change_from_baseline +
                   grocery_and_pharmacy_percent_change_from_baseline + 
                   workplaces_percent_change_from_baseline +
                   residential_percent_change_from_baseline +
                     lag_1 + lag_7 + lag_14, data = data)

# Recipe with lagged versions of mobility
recipe_lag <- recipe(new_cases ~ pop_density + retail_lag7 + grocery_lag7 + residential_lag7 + workplace_lag7 + lag_1 + lag_7 + lag_14, data = data)
```

@@

# View the test set performance for the final Lasso model
print(base_final_lasso_test_metrics)

# View variable importance for the Lasso model
vip(base_final_lasso_fit$fit$fit)

@@

# View test set performance
print(final_lasso_test_metrics)

# View variable importance
vip(final_lasso_fit$fit$fit)
```

@@

# View test set performance
print(lag_final_lasso_test_metrics)

# View variable importance
vip(lag_final_lasso_fit$fit$fit)

@@

# Combine + formatting
lasso_graphs <- plot_base_lasso + plot_lasso + plot_lag_lasso +
  plot_layout(ncol = 3, widths = c(1.5, 1.5, 1.5)) &
  theme(
    plot.margin = margin(10, 10, 10, 10),
    plot.title = element_text(size = 14, hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )

@@

# Save file
figure_file = here("results", "figures", "lasso_graphs.png")
ggsave(
  filename = figure_file,
  plot = lasso_graphs,
  width = 16, height = 5, dpi = 300
)

@@

# Finalize model with best parameters
base_final_rf_spec <- rand_forest(
  mode = "regression",
  mtry = base_tuned_rf_best$mtry,
  min_n = base_tuned_rf_best$min_n,
  trees = 500
) %>%
  set_engine("ranger", seed = rngseed)

@@

# View test set performance
print(base_final_rf_test_metrics)

@@

# Finalize model with best parameters
final_rf_spec <- rand_forest(
  mode = "regression",
  mtry = rf_best$mtry,
  min_n = rf_best$min_n,
  trees = 500
) %>%
  set_engine("ranger", seed = rngseed)

# Final workflow with tuned model
final_rf_wf <- workflow() %>%
  add_recipe(recipe_baseline) %>%
  add_model(final_rf_spec)

@@

@@

# Finalize model with best parameters
lag_final_rf_spec <- rand_forest(
  mode = "regression",
  mtry = lag_tuned_rf_best$mtry,
  min_n = lag_tuned_rf_best$min_n,
  trees = 500
) %>%
  set_engine("ranger", seed = rngseed)

# Final workflow with tuned model
lag_final_rf_wf <- workflow() %>%
  add_recipe(recipe_baseline) %>%
  add_model(lag_final_rf_spec)

@@

# View test set performance
print(lag_final_rf_test_metrics)

@@

# Combine + formatting
rf_graphs <- plot_base_rf + plot_rf + plot_lag_rf +
  plot_layout(ncol = 3, widths = c(1.5, 1.5, 1.5)) &
  theme(
    plot.margin = margin(10, 10, 10, 10),
    plot.title = element_text(size = 14, hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )

@@

# Save file
figure_file = here("results", "figures", "rf_graphs.png")
ggsave(
  filename = figure_file,
  plot = rf_graphs,
  width = 16, height = 5, dpi = 300
)
```

@@

@@

# Print final performance metrics
print(base_final_boost_metrics)
```

@@

# View tuning results and print best model metrics
boost_tune_res %>%
  collect_metrics() %>%
  print()

@@

# Final model workflow
final_boost_wf <- workflow() %>%
  add_recipe(recipe_baseline) %>%
  add_model(final_boost_spec)

@@

@@

# Final model workflow
lag_final_boost_wf <- workflow() %>%
  add_recipe(recipe_baseline) %>%
  add_model(lag_final_boost_spec)

@@

# Print final performance metrics
print(lag_final_boost_metrics)
```

@@

# Combine graphs + formatting
boost_graphs <- plot_base_boost + plot_boost + plot_lag_boost +
  plot_layout(ncol = 3, widths = c(1.5, 1.5, 1.5)) &
  theme(
    plot.margin = margin(10, 10, 10, 10),
    plot.title = element_text(size = 14, hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )

@@

# Save file
figure_file = here("results", "figures", "boost_graphs.png")
ggsave(
  filename = figure_file,
  plot = boost_graphs,
  width = 16, height = 5, dpi = 300
)

@@

base_lasso_metrics <- base_final_lasso_test_metrics %>% 
  mutate(model = "LASSO (Baseline)") %>%
  rename(mean = .estimate)

lasso_metrics <- final_lasso_test_metrics %>% 
  mutate(model = "LASSO") %>%
  rename(mean = .estimate)

lag_lasso_metrics <- lag_final_lasso_test_metrics %>% 
  mutate(model = "LASSO (Lagged Mobility)") %>%
  rename(mean = .estimate)

final_boost_metrics <- final_boost_metrics %>%
  mutate(model = "XGBoost") %>%
  rename(mean = .estimate)

final_forest_metrics <- final_rf_test_metrics %>%
  mutate(model = "Random Forest") %>%
  rename(mean = .estimate)

base_final_boost_metrics <- base_final_boost_metrics %>%
  mutate(model = "XGBoost (Baseline)") %>%
  rename(mean = .estimate)

base_final_forest_metrics <- base_final_rf_test_metrics %>%
  mutate(model = "Random Forest (Baseline)") %>%
  rename(mean = .estimate)

lag_boost_metrics <- lag_final_boost_metrics %>%
  mutate(model = "XGBoost (Lagged Mobility)") %>%
  rename(mean = .estimate)

lag_forest_metrics <- lag_final_rf_test_metrics %>%
  mutate(model = "Random Forest (Lagged Mobility)") %>%
  rename(mean = .estimate)

@@

# Pivot and remove unncessary columns
model_metrics <- model_metrics %>%
  select(-.estimator) %>%
  pivot_wider(names_from = '.metric', values_from = mean)
```

This code chunk creates a short summary table of the results from the model_metrics data frame.
```{r}
# Create gt table
model_table <- model_metrics %>%
  gt() %>%
  tab_header(
    title = "Model Performance Metrics",
    subtitle = "Best values are highlighted per metric"
  ) %>%
  fmt_number(columns = c(rmse, mae), decimals = 1) %>%
  fmt_number(columns = rsq, decimals = 3) %>%
  cols_label(
    model = "Model",
    rmse = "RMSE",
    rsq = "R²",
    mae = "MAE"
  ) %>%

>>>>

# Check date ranges
range(train_data$date)
range(test_data$date)
```

Recipe setting for modeling. Also rename the variable names.
```{r}
# Recipe for baseline model
recipe_baseline <- recipe(new_cases ~ pop_density + lag_1 + lag_7 + lag_14, data = data) %>% step_rename(
  Population_Density = pop_density,
    Lag_1_Day = lag_1,
    Lag_7_Days = lag_7,
    Lag_14_Days = lag_14
)

# Recipe with all predictors
recipe <- recipe(new_cases ~ pop_density +
                   retail_and_recreation_percent_change_from_baseline +
                   grocery_and_pharmacy_percent_change_from_baseline + 
                   workplaces_percent_change_from_baseline +
                   residential_percent_change_from_baseline +
                   lag_1 + lag_7 + lag_14, data = data) %>%
  step_rename(
    Population_Density = pop_density,
    Retail_Mobility = retail_and_recreation_percent_change_from_baseline,
    Grocery_Mobility = grocery_and_pharmacy_percent_change_from_baseline,
    Workplace_Mobility = workplaces_percent_change_from_baseline,
    Residential_Mobility = residential_percent_change_from_baseline,
    Lag_1_Day = lag_1,
    Lag_7_Days = lag_7,
    Lag_14_Days = lag_14
  )

# Recipe with lagged versions of mobility
recipe_lag <- recipe(new_cases ~ pop_density + retail_lag7 + grocery_lag7 + residential_lag7 + workplace_lag7 + lag_1 + lag_7 + lag_14, data = data) %>%
  step_rename(
    Population_Density = pop_density,
    Retail_Mobility_Lag7 = retail_lag7,
    Grocery_Mobility_Lag7 = grocery_lag7,
    Residential_Mobility_Lag7 = residential_lag7,
    Workplace_Mobility_Lag7 = workplace_lag7,
    Lag_1_Day = lag_1,
    Lag_7_Days = lag_7,
    Lag_14_Days = lag_14
  )
```

@@

# View the test set performance for the final Lasso model
print(base_final_lasso_test_metrics)
```

Collect Metrics and VIP
```{r}
# Collect CV metrics and drop extra columns
base_final_lasso_cv_metrics <- collect_metrics(base_final_lasso_res) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Train")

# Prepare Test metrics to match
base_final_lasso_test_metrics_fixed <- base_final_lasso_test_metrics %>%
  mutate(mean = .estimate) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Test")

# Combine CV and Test metrics
all_base_lasso_metrics <- bind_rows(
  base_final_lasso_cv_metrics,
  base_final_lasso_test_metrics_fixed
)

# View the final combined metrics
print(all_base_lasso_metrics)

# View variable importance for the Lasso model
vip_base_lasso <- vip(base_final_lasso_fit$fit$fit)

# Alter aesthetics
vip_base_lasso <- vip_base_lasso + labs(
  title = "Baseline LASSO Variable Importance",
  x = "Importance",
  y = "Feature"
) + theme_bw()

figure_file = here("results", "figures", "vip_base_lasso.png")
ggsave(filename = figure_file, plot = vip_base_lasso, width = 8, height = 6, dpi = 300)
```

@@

# View test set performance
print(final_lasso_test_metrics)
```

Collect Metrics and VIP
```{r}
# Collect CV metrics and drop extra columns
final_lasso_cv_metrics <- collect_metrics(final_lasso_res) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Train")

# Prepare Test metrics to match
final_lasso_test_metrics_fixed <- final_lasso_test_metrics %>%
  mutate(mean = .estimate) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Test")

# Combine CV and Test metrics
all_lasso_metrics <- bind_rows(
  final_lasso_cv_metrics,
  final_lasso_test_metrics_fixed
)

# View the final combined metrics
print(all_lasso_metrics)

# Plot VIP
vip_full_lasso <- vip(final_lasso_fit$fit$fit)

# Alter aesthetics
vip_full_lasso <- vip_full_lasso + 
  labs(
    title = "LASSO with Mobility Variable Importance",
    x = "Importance",
    y = "Feature"
  ) + 
  theme_bw()

# Define save location
figure_file <- here("results", "figures", "vip_full_lasso.png")

# Save plot
ggsave(filename = figure_file, plot = vip_full_lasso, width = 8, height = 6, dpi = 300)
```

@@

# View test set performance
print(lag_final_lasso_test_metrics)
```

Collect Metrics and VIP
```{r}
# Collect CV metrics and drop extra columns
lag_final_lasso_cv_metrics <- collect_metrics(lag_final_lasso_res) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Train")

# Prepare Test metrics to match
lag_final_lasso_test_metrics_fixed <- lag_final_lasso_test_metrics %>%
  mutate(mean = .estimate) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Test")

# Combine CV and Test metrics
all_lag_lasso_metrics <- bind_rows(
  lag_final_lasso_cv_metrics,
  lag_final_lasso_test_metrics_fixed
)

# View the final combined metrics
print(all_lag_lasso_metrics)

# Plot VIP
vip_lag_lasso <- vip(lag_final_lasso_fit$fit$fit)

# Alter aesthetics
vip_lag_lasso <- vip_lag_lasso + 
  labs(
    title = "LASSO with Lagged Mobility Variable Importance",
    x = "Importance",
    y = "Feature"
  ) + 
  theme_bw()

# Define save location
figure_file <- here("results", "figures", "vip_lag_lasso.png")

# Save plot
ggsave(filename = figure_file, plot = vip_lag_lasso, width = 8, height = 6, dpi = 300)

@@

# Combine + formatting
lasso_graphs <- plot_base_lasso + plot_lasso + plot_lag_lasso +
  plot_layout(ncol = 3, widths = c(1.5, 1.5, 1.5)) &
  theme(
    plot.margin = margin(10, 10, 10, 10),
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title = element_text(size = 18),
    axis.text = element_text(size = 16)
  )

@@

# Save file
figure_file = here("results", "figures", "lasso_graphs.png")
ggsave(
  filename = figure_file,
  plot = lasso_graphs,
  width = 18, height = 6, dpi = 400
)
```

@@

# Finalize model with best parameters
base_final_rf_spec <- rand_forest(
  mode = "regression",
  mtry = base_tuned_rf_best$mtry,
  min_n = base_tuned_rf_best$min_n,
  trees = 500
) %>%
  set_engine("ranger", seed = rngseed, importance = "impurity")

@@

# View test set performance
print(base_final_rf_test_metrics)
```

Collect metrics and VIP
```{r}
# Collect CV metrics and drop extra columns
base_final_rf_cv_metrics <- collect_metrics(base_final_rf_res) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Train")

# Prepare test metrics to match format
base_final_rf_test_metrics_fixed <- base_final_rf_test_metrics %>%
  mutate(mean = .estimate) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Test")

# Combine CV and Test metrics
all_base_rf_metrics <- bind_rows(
  base_final_rf_cv_metrics,
  base_final_rf_test_metrics_fixed
)

# Print metrics
print(all_base_rf_metrics)

# Create vip
vip_base_rf <- vip(base_final_rf_fit)

# Alter aesthetics
vip_base_rf <- vip_base_rf + 
  labs(
    title = "Baseline Random Forest Variable Importance",
    x = "Importance",
    y = "Feature"
  ) + 
  theme_bw()

# Save vip
figure_file <- here("results", "figures", "vip_base_rf.png")
ggsave(filename = figure_file, plot = vip_base_rf, width = 8, height = 6, dpi = 300)
```

@@

# Finalize model with best parameters
final_rf_spec <- rand_forest(
  mode = "regression",
  mtry = rf_best$mtry,
  min_n = rf_best$min_n,
  trees = 500
) %>%
  set_engine("ranger", seed = rngseed, importance = "impurity")

# Final workflow with tuned model
final_rf_wf <- workflow() %>%
  add_recipe(recipe) %>%
  add_model(final_rf_spec)

@@

Collect metrics and VIP
```{r}
# Collect CV metrics and drop extra columns
final_rf_cv_metrics <- collect_metrics(final_rf_res) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Train")

# Prepare test metrics to match format
final_rf_test_metrics_fixed <- final_rf_test_metrics %>%
  mutate(mean = .estimate) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Test")

# Combine CV and Test metrics
all_rf_metrics <- bind_rows(
  final_rf_cv_metrics,
  final_rf_test_metrics_fixed
)

# Print metrics
print(all_rf_metrics)

# Create vip
vip_full_rf <- vip(final_rf_fit)

# Alter aesthetics
vip_full_rf <- vip_full_rf + 
  labs(
    title = "Random Forest with Mobility Variable Importance",
    x = "Importance",
    y = "Feature"
  ) + 
  theme_bw()

# Save vip
figure_file <- here("results", "figures", "vip_full_rf.png")
ggsave(filename = figure_file, plot = vip_full_rf, width = 8, height = 6, dpi = 300)
```

@@

# Finalize model with best parameters
lag_final_rf_spec <- rand_forest(
  mode = "regression",
  mtry = lag_tuned_rf_best$mtry,
  min_n = lag_tuned_rf_best$min_n,
  trees = 500
) %>%
  set_engine("ranger", seed = rngseed, importance = "impurity")

# Final workflow with tuned model
lag_final_rf_wf <- workflow() %>%
  add_recipe(recipe_lag) %>%
  add_model(lag_final_rf_spec)

@@

# View test set performance
print(lag_final_rf_test_metrics)
```

Collect metrics and CV
```{r}
# Collect CV metrics and drop extra columns
lag_final_rf_cv_metrics <- collect_metrics(lag_final_rf_res) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Train")

# Prepare test metrics to match format
lag_final_rf_test_metrics_fixed <- lag_final_rf_test_metrics %>%
  mutate(mean = .estimate) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Test")

# Combine CV and Test metrics
all_lag_rf_metrics <- bind_rows(
  lag_final_rf_cv_metrics,
  lag_final_rf_test_metrics_fixed
)

# Print metrics
print(all_lag_rf_metrics)

# Create vip
vip_lag_rf <- vip(lag_final_rf_fit)

# Alter aesthetics
vip_lag_rf <- vip_lag_rf + 
  labs(
    title = "Random Forest with Lagged Mobility Variable Importance",
    x = "Importance",
    y = "Feature"
  ) + 
  theme_bw()

# Save vip
figure_file <- here("results", "figures", "vip_lag_rf.png")
ggsave(filename = figure_file, plot = vip_lag_rf, width = 8, height = 6, dpi = 300)
```

@@

# Combine + formatting
rf_graphs <- plot_base_rf + plot_rf + plot_lag_rf +
  plot_layout(ncol = 3, widths = c(1.5, 1.5, 1.5)) &
  theme(
    plot.margin = margin(10, 10, 10, 10),
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title = element_text(size = 18),
    axis.text = element_text(size = 16)
  )

@@

# Save file
figure_file = here("results", "figures", "rf_graphs.png")
ggsave(
  filename = figure_file,
  plot = rf_graphs,
  width = 18, height = 6, dpi = 400
)
```

@@

autoplot(base_boost_tune_res)

@@

# Print final performance metrics
print(base_final_boost_metrics)

# Extract Model
base_boost_model <- base_final_boost_fit$fit$fit
```

Collect metrics and VIP
```{r}

# select metrics from best model
base_boost_cv_metrics <- base_boost_tune_res %>%
  collect_metrics() %>%
  inner_join(base_best_params, by = c("tree_depth", "learn_rate", "loss_reduction")) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Train")

# Prepare test metrics to match format
base_final_boost_test_metrics <- base_final_boost_results %>%
  metrics(truth = truth, estimate = predicted) %>%
  mutate(mean = .estimate) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Test")

# Combine CV and Test metrics
all_base_boost_metrics <- bind_rows(
  base_boost_cv_metrics,
  base_final_boost_test_metrics
)

# Print metrics
print(all_base_boost_metrics)

# Create vip
vip_base_boost <- vip(base_boost_model)

# Alter aesthetics
vip_base_boost <- vip_base_boost + 
  labs(
    title = "Baseline XGBoost Variable Importance",
    x = "Importance",
    y = "Feature"
  ) + 
  theme_bw()

# Print
print(vip_base_boost)

# Save vip
figure_file <- here("results", "figures", "vip_base_boost.png")
ggsave(filename = figure_file, plot = vip_base_boost, width = 8, height = 6, dpi = 300)
```

@@

# View tuning results and print best model metrics
boost_tune_res %>%
  collect_metrics() %>%
  print()
autoplot(boost_tune_res)

@@

# Final model workflow
final_boost_wf <- workflow() %>%
  add_recipe(recipe) %>%
  add_model(final_boost_spec)

@@

# Extract Model
full_boost_model <- final_boost_fit$fit$fit
```

Collect metrics and VIP
```{r}
# Collect CV metrics and drop extra columns
boost_cv_metrics <- boost_tune_res %>%
  collect_metrics() %>%
  inner_join(best_params, by = c("tree_depth", "learn_rate", "loss_reduction")) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Train")

# Prepare test metrics to match format
final_boost_test_metrics <- final_boost_results %>%
  metrics(truth = truth, estimate = predicted) %>%
  mutate(mean = .estimate) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Test")

# Combine CV and Test metrics
all_boost_metrics <- bind_rows(
  boost_cv_metrics,
  final_boost_test_metrics
)

# Print metrics
print(all_boost_metrics)

# Create vip
vip_full_boost <- vip(full_boost_model)

# Alter aesthetics
vip_full_boost <- vip_full_boost + 
  labs(
    title = "XGBoost with Mobility Variable Importance",
    x = "Importance",
    y = "Feature"
  ) + 
  theme_bw()

# Save vip
figure_file <- here("results", "figures", "vip_full_boost.png")
ggsave(filename = figure_file, plot = vip_full_boost, width = 8, height = 6, dpi = 300)
```

@@

# Final model workflow
lag_final_boost_wf <- workflow() %>%
  add_recipe(recipe_lag) %>%
  add_model(lag_final_boost_spec)

@@

# Print final performance metrics
print(lag_final_boost_metrics)

# Extract Model
lag_boost_model <- lag_final_boost_fit$fit$fit
```

Collect metrics and VIP
```{r}
# Collect CV metrics and drop extra columns
lag_boost_cv_metrics <- lag_boost_tune_res %>%
  collect_metrics() %>%
  inner_join(lag_best_params, by = c("tree_depth", "learn_rate", "loss_reduction")) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Train")

# Prepare test metrics to match format
lag_final_boost_test_metrics <- lag_final_boost_results %>%
  metrics(truth = truth, estimate = predicted) %>%
  mutate(mean = .estimate) %>%
  select(.metric, .estimator, mean) %>%
  mutate(Data = "Test")

# Combine CV and Test metrics
all_lag_boost_metrics <- bind_rows(
  lag_boost_cv_metrics,
  lag_final_boost_test_metrics
)

# Print metrics
print(all_lag_boost_metrics)

# Create vip
vip_lag_boost <- vip(lag_boost_model)

# Alter aesthetics
vip_lag_boost <- vip_lag_boost + 
  labs(
    title = "XGBoost with Lagged Mobility Variable Importance",
    x = "Importance",
    y = "Feature"
  ) + 
  theme_bw()

# Print
print(vip_lag_boost)

# Save vip
figure_file <- here("results", "figures", "vip_lag_boost.png")
ggsave(filename = figure_file, plot = vip_lag_boost, width = 8, height = 6, dpi = 300)
```

@@

# Combine graphs + formatting
boost_graphs <- plot_base_boost + plot_boost + plot_lag_boost +
  plot_layout(ncol = 3, widths = c(1.5, 1.5, 1.5)) &
  theme(
    plot.margin = margin(10, 10, 10, 10),
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title = element_text(size = 18),
    axis.text = element_text(size = 16)
  )

@@

# Save file
figure_file = here("results", "figures", "boost_graphs.png")
ggsave(
  filename = figure_file,
  plot = boost_graphs,
  width = 18, height = 6, dpi = 400
)

@@

base_lasso_metrics <- all_base_lasso_metrics %>% 
  mutate(model = "LASSO (Baseline)")

lasso_metrics <- all_lasso_metrics %>% 
  mutate(model = "LASSO")

lag_lasso_metrics <- all_lag_lasso_metrics %>% 
  mutate(model = "LASSO (Lagged Mobility)")

base_final_boost_metrics <- all_base_boost_metrics %>%
  mutate(model = "XGBoost (Baseline)")

final_boost_metrics <- all_boost_metrics %>%
  mutate(model = "XGBoost")

lag_boost_metrics <- all_lag_boost_metrics %>%
  mutate(model = "XGBoost (Lagged Mobility)")

base_final_forest_metrics <- all_base_rf_metrics %>%
  mutate(model = "Random Forest (Baseline)")

final_forest_metrics <- all_rf_metrics %>%
  mutate(model = "Random Forest")

lag_forest_metrics <- all_lag_rf_metrics %>%
  mutate(model = "Random Forest (Lagged Mobility)")

@@

# Pivot and remove unncessary columns
model_metrics <- model_metrics %>%
  select(-.estimator) %>%
  pivot_wider(names_from = c('.metric', 'Data'), values_from = mean)
```

```{r}
model_table <- model_metrics %>%
  select(model, rmse_Train, mae_Train, rsq_Train, rmse_Test, mae_Test, rsq_Test) %>%
  gt() %>%
  tab_header(
    title = "Model Performance Metrics",
    subtitle = "Train and Test Results | Best Performance Highlighted in Green"
  ) %>%
  fmt_number(columns = everything(), decimals = 3) %>%
  cols_label(
    model = "Model",
    rmse_Train = "RMSE",
    mae_Train = "MAE",
    rsq_Train = "R²",
    rmse_Test = "RMSE",
    mae_Test = "MAE",
    rsq_Test = "R²"
  ) %>%
  tab_spanner(
    label = "Train Metrics",
    columns = c(rmse_Train, mae_Train, rsq_Train)
  ) %>%
  tab_spanner(
    label = "Test Metrics",
    columns = c(rmse_Test, mae_Test, rsq_Test)
  ) %>%
  tab_style(
    style = cell_fill(color = "lightgreen"),
    locations = cells_body(
      columns = rmse_Test,
      rows = rmse_Test == min(rmse_Test, na.rm = TRUE)
    )
  ) %>%
  tab_style(
    style = cell_fill(color = "lightgreen"),
    locations = cells_body(
      columns = mae_Test,
      rows = mae_Test == min(mae_Test, na.rm = TRUE)
    )
  ) %>%
  tab_style(
    style = cell_fill(color = "lightgreen"),
    locations = cells_body(
      columns = rsq_Test,
      rows = rsq_Test == max(rsq_Test, na.rm = TRUE)
    )
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything())
  ) %>%
  tab_options(
    table.width = pct(100),
    table.align = "left",
    column_labels.padding = px(10),
    data_row.padding = px(6)
  )

This code chunk creates a short summary table of the results from the model_metrics data frame.
```{r}
# Create gt table
model_table <- model_metrics %>%
  gt() %>%
  tab_header(
    title = "Model Performance Metrics on Data",
    subtitle = "Best values are highlighted per metric"
  ) %>%
  fmt_number(columns = c(rmse, mae), decimals = 1) %>%
  fmt_number(columns = rsq, decimals = 3) %>%
  cols_label(
    model = "Model",
    rmse = "RMSE",
    rsq = "R²",
    mae = "MAE"
  ) %>%
